Multi-level Selective Deduplication for VM Snapshots in Cloud Storage

### 2012-03-10 vm_snapshot_sim/2012arch.tex
final

Base on the Zipf-like distribution pattern, many previous analysis and result on web caching may apply.
In general this indicates a small set of popular data dominates data duplication.
Although we already know OS-related data are heavily duplicated among OS disks, 
it still surprises us that user-related data follow a similar pattern.
Therefore, we collect the CDS by performing global reference counting through map-reduce for all
blocks in snapshot store, and select the most popular ones base on the memory limitation of
CDS hash index.

The CDS collected from user-related data is generally proportional to the data size.
As discussed in Section~\ref{sect:exper}, selecting about 1\% of data (after level 1 and level 2 deduplication)
can cover about 38\% of data blocks. Consider we allow maximum 25 VMs per machine, each VM has
about 30GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
each backup is 10\%, this translates to 15GB CDS data per machine, and the 
memory cost by CDS hash index is about 150MB per machine.
On the other hand, the CDS from OS-related data is only relvant to the number of OS releases.
Our experiment on 7 major OS releases shows that about 100GB of data is never modified, and we expect
it won't grow over 200GB in the near future. So it would cost the entire cluster 2GB of memory to
store its hash index, or 20MB per machine on a 100 node cluster. On average each OS disk has about 10GB
of data that can be completely eliminated in this way.
\comments{
As the number of VMs increases, the popularity of common blocks for data disks changes.
But this increase has a small impact on OS block popularity because 
there are a limited number of OS releases used by VMs. We let CDS cover the common OS blocks first and
our CDS selection strategy is designed as follows.

>>>>

Base on the Zipf-like distribution pattern, many previous analysis and results on web caching may apply.
In general this indicates a small set of popular data dominates data duplication.
Although we already know OS-related data are heavily duplicated among OS disks, 
it still surprises us that user-related data follow a similar pattern.
Therefore, we collect the CDS by performing global reference counting through map-reduce for all
blocks in snapshot store, and select the most popular ones base on the memory limitation of
CDS hash index.

The CDS collected from user-related data is generally proportional to the data size.
As discussed in Section~\ref{sect:exper}, selecting about 1\% of data (after level 1 and level 2 deduplication)
can cover about 38\% of data blocks. Consider we allow maximum 25 VMs per machine, each VM has
about 30GB of user-related data, having 10 snapshots in its snapshot store and the data change ratio during
each backup is 10\%, this translates to 15GB CDS data per machine. 
Consider each CDS hash index entry cost about 40 bytes and the average block size is 4KB, this leads to
a 1:100 ratio so the 
memory cost by CDS hash index is about 150MB per machine.
On the other hand, the CDS from OS-related data is only relvant to the number of OS releases.
Our experiment on 7 major OS releases shows that about 100GB of data is never modified, and we expect
it won't grow over 200GB in the near future. So it would cost the entire cluster 2GB of memory to
store its hash index, or 20MB per machine on a 100 node cluster. On average each OS disk has about 10GB
of data that can be completely eliminated in this way.
\comments{
As the number of VMs increases, the popularity of common blocks for data disks changes.
But this increase has a small impact on OS block popularity because 
there are a limited number of OS releases used by VMs. We let CDS cover the common OS blocks first and
our CDS selection strategy is designed as follows.

### 2012-03-10 vm_snapshot_sim/2012concl.tex
final

\section{Conclusion}
\label{sect:final}
The main contribution of this paper is a multi-level selective deduplication scheme among VM snapshots. 
Inner-VM deduplication localizes backup data dependence and exposes more parallelism  
while global deduplication using a small common data set appeared in OS and data disks
effectively  covers a large amount of snapshot blocks.
Our evaluation using Aliyun's data has shown that 
level 1 and level 2 deduplication can reduce the storage need by 78\% while level 2 inner 
fingerprint comparsion contributes 4.5\%%. 
Level 3 can add additional 10.5\% reduction and accomplish 75\% of what full fingerprint-based
deduplication can do. Our scheme uses a very small amount of memory on each node, and leaves
room for additional optimization we are further studying.
%Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
%this is about 600 terabytes.

>>>>

\section{Conclusion}
\label{sect:final}
In this paper we propose a multi-level selective deduplication scheme for 
snapshot service in VM cloud. 
Inner-VM deduplication localizes backup data dependency and exposes more parallelism  
while cross-VM deduplication with a small common data set
effectively  covers a large amount of duplicated data.
Our solution accomplishes the majority of
potential global deduplication saving while still meets stringent cloud resources requirement. 
Evaluation using real user's VM data shows
our solution can accomplish 75\% of what complete global
deduplication can do. 
Compare to today's widely-used snapshot technique, our scheme reduces almost
two-third of snapshot storage cost.
Our scheme uses a very small amount of memory on each node, and leaves
room for additional optimization we are further studying.
%Noted that 6\% is still significant, which is about 24GB per each VM and for a 1000 node Aliyun cluster,
%this is about 600 terabytes.

### 2012-03-10 vm_snapshot_sim/2012eval.tex
final

We have implemented a snapshot deduplication scheme on the Aliyun's cloud platform.
Our experimental evaluation has the following two objectives:
1) Analyze the commonality of content data blocks and the popularity  of hot items. We 
examine the impacts of CDS size on deduplication ratio.
2) Assess the effectiveness  of 3-level deduplication for reducing the storage requirement of snapshot 
backup.

@@

An Aliyun our target is to backup cluster with 1000 nodes
with 25 VMs on each.
We are running our deduplication/backup  service on 100 nodes.
Memory usage is about 150MB space per node during backup and
the CPU usage is very small during the experiments. 
Based on the data studied,  each VM has about  40GB of storage  data usage on average,
OS disk and data disk each takes about 50\% of storage space.
The backup of VM snapshots is completed within two hours  every day,
and that translates to a backup throughput of 139GB per second, or 500TB per hour.
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.

@@

We have used a storage dataset of  1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated 
is 23.5 terabytes.
Each VM file is  divided into content blocks of
variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using  their SHA-1 hash. 
Each segment is of size 2MB.  
Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
CDS every 1-2 days to catch up the popularity trend.

%seg, and we performed global perfect deduplication 
%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
%and maximum block size
%OS data
%user data: zipf
%prediction
%say something about aliyun

@@

Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication.
The X axis shows the overall impact in (a),  impact on OS disk in (b), and impact on data disk in (c).
Each bar in the Y axis shows the data size after deduplication divided by the original data size.
Level-1 elimination can reduce the data size to about 22\% of original data, namely it delivers close 78\% reduction.
Level-2 elimination applied after level 1
reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
Level-3 elimination together with level 1 and 2
reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.

@@

To see the impact of multi-level deduplication on different OS releases, we choose 7 major OSes in Aliyun's
VM cloud platform and they are: 
Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
distributions are 64 bits).
Then we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
owners. 
%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
In this experiment, we tag each block as  ``new''
if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot block store;
``CDS''  if this block can be found  in CDS;
``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
``Parent block'' if  this block is marked unchanged in parent's block recipe.
With this tagging, we compute the percentage of duplication accomplished by level-1 inner VM deduplication,
level-2 inner VM deduplication and level 3 cross-VM deduplication.
As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination
this is because the time interval between two snapshots in our dataset
is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
contributing about about 10\% of reduction on average.

@@

\comments{
\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}
\epsfig{file=images/datadisk.count_rank.eps, width=3.5in}
\caption{Duplicate count  of common data blocks in a log scale.}
\label{fig:zipf-data}
\end{figure}
Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in a log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.

@@

We further study how CDS covers content blocks used in image files using 90\% of
the collected dataset.
Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
The $X$ axis is the rank of common user data blocks.
Let $S_i$ and $F_I$ be the size and duplicate count 
of the $i$-th block ranked by its duplicate rank.  Then $Y$ axis is the coverage of
the common dataset covering data items from rank 1 to rank $i$. Namely  
\[
\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}.
\]

Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
appeared in in all data snapshots. The corresponding CDS index uses about 150MB memory per machine.

@@

Because there are a limited number of OS releases supported by Aliyun, we study common blocks  among
OS disks loaded with  the same OS release. 
%The selection of CDS is completed by separating OS disk and data disk.
%While block commonality among data disks may be affected in some degree
% when we scale up the number of total VMs  to be supported,
%we expect that  the block commonality among OS disks still remains to be high and  
%%can be well covered by a fixed CDS because users still adopt common OS releases.
%we choose 7 major OSes in Aliyun's
%VM cloud platform and they are: 
%Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
%distributions are 64 bits).
%we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
%owners. Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
%their OS disks. 
%For example, some Ubuntu OS disks have only 2GB of data while some have 50GB.
%For each OS, the base image and all OS
%disk snapshots are divided into variable-sized blocks. Then 
In  Figure~\ref{fig:OSunchanged},  we list a conservative  commonality study in 7 major OS versions  supported
in Aliyun.  We consider the earlier snapshot for each OS disk as the base image.
For every block in the base image, we classify this block as ``completely common''
if  this block has appeared in all snapshots of the same OS release even they are used by different VMs.
Figure \ref{fig:OSunchanged} shows that for each
OS,  at least 70\% of OS blocks are completely common among all snapshots of the same OS. 
Some latest release  of OS tends to have a higher percentage of content change
while  old release tends to have more variations of content versions.
That can be interpreted as that users with very old  version of operating systems
have a lower tendency to update their OS versions and this causes a larger discrepancy
among OS snapshots of these users.

@@

Based on the above analysis, we have selected a small set of most popular
OS blocks, which is about 100GB OS data and its corresponding CDS index takes about 1GB memory space in total.
They can cover sufficiently over 70\% of OS blocks.

@@

\subsection{A comparison of perfect and CDS-based deduplication }
%Figure~\ref{fig:pd} shows the compression ratio of perfect deduplication at different dataset sizes
%as we vary the data size from about 4 terabytes to about 23.5 terabytes.
After level-1 and level 2 elimination, our experiment shows that 
the full deduplication would reduce the storage  further   by  45\% to 53\% of user disk space. 
If we put all these unique data into CDS, we could achieve full deduplication,
but the CDS size is not affordable. So we evaluate how much space saving of 
deduplication can be achieved when varying the CDS size.
%\begin{figure}
%  \centering
%  \epsfig{file=images/dedup_ratio.eps, height=2in, width=2.66in}
%  \caption{Perfect deduplication on data disks}
%  \label{fig:pd}
%\end{figure}

%We rank unique data blocks by their duplication count, and choose the hottest blocks as CDS. 
Figure \ref{fig:datacdssize} shows the relationship between CDS cache size and relative space saving ratio
compared to the full deduplication.  The unit of CDS size is gigabytes.
We define \emph{space saving ratio} as the space saving of the CDS method divided by 
full deduplication saving ratio. 
With a 100GB CDS data (namely 1GB CDS index) can still  accomplish about 75\% 
of what perfect deduplication can do.
%But this effect decreases when more data are added to CDS. 
%The lower bound of CDS space saving ratio is 50\%, which is very easy to accomplish.

@@

%CDS size is restricted by system memory resource.
Figure \ref{fig:datacds} shows how CDS space saving ratio
compared to the full deduplication is affected by the dataset size. 
The calculation is done after level 1 and level 2 deduplication.
$X$ axis uses the data size collected  from up to 1323 VMs, which occupies about
53 machines. 
In this experiment we first set out a goal of space saving ratio completed, 
then watch how much data needs to be placed in CDS cache to achieve this goal.
From the graph we can see a 75\% saving ratio lead to a stable ratio between 
CDS size and data size, which requires 1\% of data to be placed in CDS.

When we deal with a cluster of 1,000 nodes, we expect that using
1\% of data disks can cover more what we have seen from this
1323 VM dataset, assuming that the average behavior of every subcluster with 53 machines
exhibits a similar commonality. 
In addition to this, CDS for OS disks will become even more effective when
there are more VMs sharing the same collection of OS releases. 
%Base on above data we can estimate the size of data CDS and its effect. 
%Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
%If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
% maintain 10 snapshots per VM, each brings 10\% additional modified data. 
%Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
%$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.

>>>>

We have implemented the snapshot deduplication scheme on the Aliyun's cloud platform.
Objectives of our experimental evaluation are:
1) Analyze the commonality of content data blocks and the popularity  of hot items. 
2) Assess the effectiveness  of 3-level deduplication for reducing the storage cost of snapshot 
backup. 
3) Examine the impacts of CDS size on deduplication ratio.

@@

At Aliyun our target is to backup cluster up to 1000 nodes
with 25 VMs on each.
%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
Based on the data studied,  each VM has about  40GB of storage  data usage on average,
OS disk and data disk each takes about 50\% of storage space.
The backup of VM snapshots is completed within two hours every day,
and that translates to a backup throughput of 139GB per second, or 500TB per hour.
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.

@@

Since it's impossible to perform large scale analysis without affecting the VM performance,
we sampled two data sets from real user VMs to measure the effectiveness of our deduplication scheme.
Dataset1 is used study the detail impact of 3-level deduplication process,
it compose of 35 VMs from 7 popular OSes: 
Debian, Ubuntu, Redhat, CentOS, Win2003 32bit, win2003 64 bit and win2008 64 bit. For each OS, 
5 VMs are chosen, and every VM come with 10 full snapshots of it OS and data disk. 
The overall data size for this 700 full snapshots is 17.6 TB.

Dataset2 contains the first snapshots of 1323 VMs' data disks from a small cluster with 100 nodes. 
Since inner-VM deduplication is not involved in the first snapshot, this data set helps us to 
study the CDS deduplication against user-related data. The overall size of dataset2 is 23.5 TB.

All data are divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks ~\cite{similar94,rabin81} with an average size of 4KB.
The signature for variable-sized blocks is computed using their SHA-1 hash. 
Popularity of data blocks are collected through global counting 
and the top 1\% will fall into CDS, as discussed in Section~\ref{sect:crossVM}.

\comments{
a storage dataset of 1323 VM users collected from 100 Aliyun's cloud nodes to evaluate the effectiveness.
In this dataset, there are 10 snapshots per each VM user and the total amount of space investigated 
is 23.5 terabytes.
Each VM file is  divided into content blocks of
variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using  their SHA-1 hash. 
Each segment is of size 2MB.  
Popularity is computed by using 90\% of dataset, which reflects our setting that the system recomputes
CDS every 1-2 days to catch up the popularity trend.
}
%seg, and we performed global perfect deduplication 
%to caculate the number of duplicate copies of each individual unique block. We choose 2KB, 4KB, 16KB as the minimum, average
%and maximum block size
%OS data
%user data: zipf
%prediction
%say something about aliyun

@@

Figure~\ref{fig:overall} shows the overall impact of 3-level deduplication on dataset1.
The X axis shows the overall impact in (a),  impact on OS disks in (b), and impact on data disks in (c).
Each bar in the Y axis shows the data size after deduplication divided by the original data size.
Level-1 elimination can reduce the data size to about 22\% of original data, namely it delivers close 78\% reduction.
Level-2 elimination is applied to data that could pass level-1, it
reduces the size further to about 18.5\% of original size, namely it delivers additional 4.5\% reduction.
Level-3 elimination together with level 1 and 2
reduces the size further to 8\% of original size, namely it delivers additional 10.5\% reduction.
Level 2 elimination is more visible in OS disk than data disk, because data change frequency is really small
when we sample last 10 snapshots of each user in 10 days. Nevertheless, the overall impact of level 2 is still significant.
A 4.5\% of reduction from the original data represents about 450TB space saving for a 1000-node cluster.

@@

%To see the impact of multi-level deduplication on different OS releases,
%Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
Figure~\ref{fig:oscds} shows the impact of different levels of deduplication for different OS releases.
In this experiment, we tag each block in 350 OS disk snapshots from dataset1 as  ``new''
if this block cannot be deduplicated by our scheme and thus has to be written to the snapshot store;
``CDS''  if this block can be found  in CDS;
``Parent segment'' if  this block is marked unchanged in parent's segment recipe.
``Parent block'' if  this block is marked unchanged in parent's block recipe.
With this tagging, we compute the percentage of deduplication accomplished by each level.
As we can see from Figure~\ref{fig:oscds}, level-1 deduplication accomplishes a large percentage of elimination,
this is because the time interval between two snapshots in our dataset
is quite short and the Aliyun cloud service makes a snapshot  everyday  for each VM.
On the other hand,  CDS still finds lots of duplicates that inner VM deduplication can't find,
contributing about about 10\% of reduction on average.

It is noticable that level-1 deduplication doesn't work well for CentOS, a significant percentage of data is not
eliminated until they reach level-3. It shows that even user upgrade his VM system heavily and frequently
such that data locality is totally lost, those OS-related data can still be identified at level-3.

In gengral we see a stable data reduction ratio for all OS varieties, ranging from 92\% to 97\%, that means
the storage cost of 10 full snapshots combined is still smaller than the original disk size. And compare to 
today's widely used copy-on-write snapshot technique, which is similar to our level-1 deduplication, our
solution cut the snapshot storage cost by 64\%.

@@

\comments{
\begin{figure}[htbp]
\centering
%\epsfig{file=images/log-log.disk.eps, height=2in, width=2.66in}
%\epsfig{file=images/log-log.disk.eps, width=3in}
\epsfig{file=images/datadisk.count_rank.eps, width=3.5in}
\caption{Duplicate count  of common data blocks in a log scale.}
\label{fig:zipf-data}
\end{figure}
Figure \ref{fig:zipf-data} shows the duplicate count  for different data blocks sorted by their ranking in 
terms of the duplication count. $Y$ axis is the popularity of a data block in log scale 
measured its duplicate count among snapshots. $X$ axis is the identification of data blocks in a log scale
sorted by their duplicate rank.  The rank number  1  is the block with the highest number of duplicates.
The curve exhibits that the popularity of common data blocks partially follows a  Zipf-like distribution.

@@

One of our biggest advantage is small memory footprint for deduplication, because we only
eliminate a small amount of highly popular data.
we use dataset2 to demostrate the coverage of popular data blocks on user-related data, 
as shown in Figure \ref{fig:userdatacoverage}.
%content blocks used in image files using 90\% of
%the collected dataset.
%Figure \ref{fig:userdatacoverage} shows the cumulative coverage  ratio of  popular common user data blocks. 
The $X$ axis is the rank of cmomon user data blocks, and $Y$ shows how much raw data can be covered given
the size of CDS.
Let $S_i$ and $F_I$ be the size and duplicate count 
of the $i$-th block ranked by its duplicate rank.  Then $Y$ axis is the coverage of
the common dataset covering data items from rank 1 to rank $i$. Namely  
\[
\frac{ \sum_{i=1}^{i} S_i * F_i} {\mbox{Total data size}}.
\]

Thus with about 1\% of blocks on data disks, CDS can cover about 38\% of total data blocks
appeared in in all data snapshots. The corresponding CDS index uses no more than 150MB memory per machine,
which can be easily co-located with other cloud services.

@@

Because there are a limited number of OS releases, we study common blocks among
OS disks loaded with  the same OS release. 
%The selection of CDS is completed by separating OS disk and data disk.
%While block commonality among data disks may be affected in some degree
% when we scale up the number of total VMs  to be supported,
%we expect that  the block commonality among OS disks still remains to be high and  
%%can be well covered by a fixed CDS because users still adopt common OS releases.
%we choose 7 major OSes in Aliyun's
%VM cloud platform and they are: 
%Win2008 Server 64 bits, Win2003 Server 32 bits, Win2003 Server 64 bits, RHEL, CentOS, Ubuntu Server and Debian (all Linux
%distributions are 64 bits).
%we examine 5 VM user disks from each OS, and 10 snapshots for each VM. These VMs have been actively used by their
%owners. Some of  OS disks are modified frequently and in some cases,  users even store a large amount of user data on
%their OS disks. 
%For example, some Ubuntu OS disks have only 2GB of data while some have 50GB.
%For each OS, the base image and all OS
%disk snapshots are divided into variable-sized blocks. Then 
In  Figure~\ref{fig:OSunchanged},  we list a conservative  commonality study in 7 major OS versions  supported
in Aliyun.
%We consider the earlier snapshot for each OS disk as the base image.
For every block in the base image, we classify this block as ``unchanged''
if this block has appeared in all snapshots of the same OS release even they are used by different VMs.
Figure \ref{fig:OSunchanged} shows that for each
OS,  at least 70\% of OS blocks are completely unchanged among all snapshots of the same OS. 
Some latest release  of OS tends to have a higher percentage of content change
while  old release tends to have more variations of content versions.
That can be interpreted as that users with very old  version of operating systems
have a lower tendency to update their OS versions and this causes a larger discrepancy
among OS snapshots of these users.

@@

Based on the above analysis, we have selected a small set of most popular
OS blocks, which is about 100GB OS data and its corresponding CDS index takes about 1GB memory space in total.
They can cover sufficiently over 70\% of OS-related data.

@@

\subsection{A comparison of perfect and CDS-based deduplication }
%Figure~\ref{fig:pd} shows the compression ratio of perfect deduplication at different dataset sizes
%as we vary the data size from about 4 terabytes to about 23.5 terabytes.
After level-1 and level 2 elimination, we find that 
the complete deduplication would reduce the storage cost further by 50\%. 
If we put all these unique data into CDS, 
we could achieve complete deduplication,
but fingerprint lookup in such huge CDS hash index would become a bottleneck as discussed in many pervious works. 
So we use dataset2 to evaluate how much space saving of 
deduplication can be achieved when varying the CDS size.
%\begin{figure}
%  \centering
%  \epsfig{file=images/dedup_ratio.eps, height=2in, width=2.66in}
%  \caption{Perfect deduplication on data disks}
%  \label{fig:pd}
%\end{figure}

%We rank unique data blocks by their duplication count, and choose the hottest blocks as CDS. 
Figure \ref{fig:datacdssize} shows the relationship between CDS cache size and relative space saving ratio
compared to the full deduplication.  The unit of CDS size is gigabytes.
We define \emph{space saving ratio} as the space saving of CDS method divided by 
full deduplication space reduction. 
With a 100GB CDS data (namely 1GB CDS index) can still  accomplish about 75\% 
of what perfect deduplication can do.
%But this effect decreases when more data are added to CDS. 
%The lower bound of CDS space saving ratio is 50\%, which is very easy to accomplish.

@@

%CDS size is restricted by system memory resource.
With dataset2, Figure \ref{fig:datacds} shows how CDS space saving ratio
compared to the full deduplication is affected by the dataset size. 
%The calculation is done after level 1 and level 2 deduplication.
In this experiment we first set out a goal of space saving ratio completed, 
then watch how much data needs to be placed in CDS cache to achieve this goal.
From the graph we can see a 75\% saving ratio lead to a stable ratio between 
CDS size and data size, which requires 1\% of data to be placed in CDS.

When we deal with a large cluster of 1,000 nodes, we expect that using
1\% of data disks can cover more than what we have seen from this
1323 VM dataset, assuming that the average behavior of every subcluster with 100 machines
exhibits a similar commonality. 
In addition to this, CDS for OS disks will become even more effective when
there are more VMs sharing the same collection of OS releases. 
%Base on above data we can estimate the size of data CDS and its effect. 
%Currently we prepared 500MB memory per machine to store CDS meta, then it can represent 50GB of data. 
%If we assume each VM has 30GB of user data at runtime, and we host 25 VMs per machine, 
% maintain 10 snapshots per VM, each brings 10\% additional modified data. 
%Thus the user data in snapshot system is 1.5TB per machine. So the upper bound of 
%$CDS size/ Data size = 0.033$, which is sufficient for the 75\% saving goal.
